A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-29 paper/paper.tex
header fix

To motivate this work, let us consider an encoding of a fragment of
Martin-L\"of's extensional, polymorphic type theory (MLTT~1979) in the logical
framework (see \cite{Martin-Lof-1979} for a full presentation). The syntax
contains two sorts, $\sortval$ (for canonical forms) and $\sortexp$ (for
non-canonical forms), and is defined in the following LF signature:
\footnote{LF signatures are presented in the style of inference rules for
  clarity. Object judgement forms have a \emph{mode} which expresses which
  arguments represent inputs, and which represent outputs; in our presentation,
  we color the inputs \emph{\InputMode\InputModeColorName}, and the outputs
  \emph{\OutputMode\OutputModeColorName}. Proper assignment of modes may be
used to construe a judgement as having algorithmic content.}

@@

\subsection{Sploosion and Refraction}

@@

First, functionality premises no longer need be directly included in
every rule which uses hypothetico-general judgement. These are
factored out into a separate judgement which has a compositional
definition (the functional sequent judgement). Because of this, the
rules in the LF will look very much like how they did in
Mpartin-L\"of's informal presentation.

>>>>

To motivate this work, let us consider an encoding of a fragment of
Martin-L\"of's extensional, polymorphic type
theory\cite{Martin-Lof-1979} in the logical framework. The syntax
contains two sorts, $\sortval$ (for canonical forms) and $\sortexp$
(for non-canonical forms), and is defined in the following LF
signature:\footnote{LF signatures are presented in the style of
inference rules for clarity. Object judgement forms have a \emph{mode}
which expresses which arguments represent inputs, and which represent
outputs; in our presentation, we color the inputs
\emph{\InputMode\InputModeColorName}, and the outputs
\emph{\OutputMode\OutputModeColorName}. Proper assignment of modes may
be used to construe a judgement as having algorithmic content.}

@@

\subsection{Extensionality}

@@

First, functionality premises no longer need be directly included in
every rule which uses hypothetico-general judgement. These are
factored out into a separate judgement which has a compositional
definition (the functional sequent judgement). Because of this, the
rules in the LF will look very much like how they did in
Martin-L\"of's informal presentation.
